Toronto Apartment Evaluations

### 2022-02-04 outputs/paper/paper.Rmd
First model added

Home safety evaluations are neccesary to protect residents from potential hazards which may lead to personal injury if left unchecked. In a city like Toronto, where a lot of people do not own their personal property and live in rented apartments, it is critical that the landlord is kept informed of their building's condition so that they can ensure a tenants safety.

@@

# ```{r bills, fig.cap="Bills of penguins", echo = FALSE}
# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = FALSE) +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
# ```

@@

@@

# This needs to be about the random data tha tI sasmpled?
# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = FALSE) +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
```

Talk way more about it.

@@

# References

>>>>

Home safety evaluations are neccesary to protect residents from potential hazards which may lead to personal injury if left unchecked. In a city like Toronto, where a lot of people do not own their personal property and live in rented apartments, it is critical that the landlord is kept informed of their building's condition so that they can ensure a tenants safety. Dhekte hein ki kuch badiya sa milta hai ya nahi inn socres ke baare mein. Aayie shuru karte, bina kisi rukawat ke.

I think we should see which factors have the most effect on the evaluation score.

@@

@@

sapply(data, class)
data[,1:5] <- sapply(data[,1:5], as.numeric)
data[,7:7] <- sapply(data[,7:7], as.numeric)
data[,10:11] <- sapply(data[,10:11], as.numeric)
data[,13:13] <- sapply(data[,13:13], as.numeric)
data[,14:35] <- sapply(data[,14:35], as.numeric)

@@

#unique proerty types
unique_properties <- unique(data$PROPERTY_TYPE)

data %>%
  ggplot(mapping = aes(x = SCORE, y = CONFIRMED_UNITS, color= WARDNAME)) + 
  geom_point(alpha = 0.5)

data %>%
  ggplot(mapping = aes(y = SCORE, fill=WARDNAME)) +
  geom_bar()

mut_data <- data %>%
  mutate(score_category =
           case_when(SCORE <= 50 ~ "<=50",
                     SCORE <= 65 ~ "51-65",
                     SCORE <= 85 ~ "66-85",
                     SCORE <= 100 ~ "86-100"),
         score_category = factor(score_category,
                                 levels = c("<=50",
                                            "51-65",
                                            "66-85",
                                            "86-100"
                                            )
                                 )
         )
view(mut_data)
mut_data %>%
  ggplot(mapping = aes(x = score_category, fill = PROPERTY_TYPE)) +
  geom_bar(position = "dodge")
```

We can see how there are a lot of apartment building with a score thats between 66 and 85, which means they wont be evaluated for the next 2 years and are consiered to be in good condition overall. But what makes the score of these buildings higher than the rest? And what do the few buildings with a score of more than 86 do that separtes them from the rest?

@@

# References
https://www.toronto.ca/community-people/housing-shelter/rental-housing-tenant-information/rental-housing-standards/apartment-building-standards/rentsafeto-for-tenants/

https://www.toronto.ca/community-people/housing-shelter/rental-housing-tenant-information/rental-housing-standards/apartment-building-standards/rentsafeto-for-building-owners/rentsafeto-building-evaluations-and-audits/
